### 2013-03-15 paper.tex
mais mudancas

\nocite{Fabbri:2002}
\addcontentsline{toc}{section}{Refer\^{e}ncias}
\bibliographystyle{ieeetr}
\bibliography{personal,strings,shading,multiview,motion,Kimia,catagorization,edge-linking,deformable,medical,graphics,active-contours,texture,imaging,tracking,shape-papers,bib-header,video,math-books,math,psych-books,metric,edge,leymarie_pami_scaffold,vision-books,vision,nn-search,multidimscaling,psychophysics,indexing,segmentation,image-databases,shape-matching,neuro,skeleton,skeleton2D,aspect-graphs,recognition,surface-networks,ridge,proceedings,perceptual-grouping,continuation,graph-matching-2,cooper}
%\input{paper.bbl}

>>>>

\nocite{Fabbri:2002}
\addcontentsline{toc}{section}{Refer\^{e}ncias}
\bibliographystyle{ieeetr}
\bibliography{personal}
%,strings,shading,multiview,motion,Kimia,catagorization,edge-linking,deformable,medical,graphics,active-contours,texture,imaging,tracking,shape-papers,bib-header,video,math-books,math,psych-books,metric,edge,leymarie_pami_scaffold,vision-books,vision,nn-search,multidimscaling,psychophysics,indexing,segmentation,image-databases,shape-matching,neuro,skeleton,skeleton2D,aspect-graphs,recognition,surface-networks,ridge,proceedings,perceptual-grouping,continuation,graph-matching-2,cooper}
%\input{paper.bbl}
